Project-plan

### 2025-11-13 manuscript.qmd
Adding flowchart to results

@@

(a) Report numbers of individuals at each stage of study—eg numbers
potentially eligible, examined for eligibility, confirmed eligible,
included in the study, completing follow-up, and analysed

(c) Consider use of a flow diagram

>>>>

<!-- (a) Report numbers of individuals at each stage of study—eg numbers
potentially eligible, examined for eligibility, confirmed eligible,
included in the study, completing follow-up, and analysed

(c) Consider use of a flow diagram -->

 ```{r main, echo=FALSE}
library(DiagrammeR)
library(glue)
source("main.R") ## This "imports" the main script file of your project and run any code in it

# Flowchart figure -----------------------------------------------------------

## Labels for figure ---------------------------------------------------------

label_A <- glue("Trauma registry 2012–2023\n{_n_total_merged_data} patients")
label_B <- glue("Identified TBI using AIS 1xxxxx.x\n{n_tbi_TBI_only_data} patients with TBI")
label_C <- glue("Excluded:\n<18 years: {n_under18}\nDead on arrival: {n_doa}")
label_D <- glue("Linked with trauma care quality database\nExcluded: no OFI outcome: {n_no_ofi}")
label_E <- glue("Complete-case selection\nExcluded: missing data in covariates: {n_missing_cc}")
label_F <- glue("Final analytic cohort\n{n_final} adult TBI patients\nOFI: {n_ofi} ({round(100*n_ofi/n_final,1)}%) | No OFI: {n_final - n_ofi}")

## Render flowchart ----------------------------------------------------------

grViz(glue("
digraph TBI_flow {{

graph [rankdir = TB]

node [shape = box, 
fontname = 'Times New Roman', 
fontsize = 12, 
width = 3]

A [label = '{label_A}']
B [label = '{label_B}']
C [label = '{label_C}']
D [label = '{label_D}']
E [label = '{label_E}']
F [label = '{label_F}']

A -> B -> C -> D -> E -> F
}}
"))

```

@@

### 2025-11-13 project-plan.qmd
Clarifying TBI def
Adding flowchart to results

TBI remains a challenge within modern trauma systems, not only due to its contribution to mortality but also due to
the magnifying impact on the outcome because of small process deviations. Delays in imaging, inconsistent airway
management, and lapses in haemodynamic measures are all examples that can result in irreversible damage. Although
TQIP have been developed to identify and correct such lapses, with the WHO stressing the importance of linking OFIs
to corrective actions and verification of bettered outcomes, most research has been done on mixed trauma cohorts.
This, on the other hand, leaves TBI-specific vulnerabilities undercharacterised. Recent work by *Szolnoky et al.*
suggests that, despite overall declines in OFI, patients with TBI remain at risk of preventable shortcomings,
underscoring the need for TBI-specific quality improvement efforts [@Szolnoky2025]. <!--CP: Therefore we hypothesis ze that is possible to identify new OFis related to TBI?? 
CP: See if something like that can be a hypothesis -->

Aim
=====
This study aims to identify and describe OFI in the care of adult trauma patients with TBI, and to examine patient- and process-related factors associated with their occurrence. <!-- CP: You need to phrase these aims in a more concrete way: this what this course demands..see also next comment E.g. (but for your supervisor to help with) Identify specific OFI by doing what? I mean , an identification require that certain parameters will be used and confirmed
If too long M&M will describe these parameters)” -->

<!-- CP: Pls describe this aim in a Yes/No question e..g determine whether the identified OFI are associated with patient and process related factors. Ask for your supervisor to help revising -->

<!--CP: Can you explain more concretely What this means? Occurrence of OPI?-->

@@

Participants
------------
Included in the study were all adult patients with TBI recorded in the Karolinska trauma registry between 2012 and
2023 who also had been screened for opportunity for improvements. Furthermore, TBI was defined as a Glasgow Coma
Scale (GCS) score of ≤8 combined with an Abbreviated Injury Scale (AIS) ≥3 for the head region. Patients were
eligible irrespective of level of care and were not restricted to intensive care admissions.

>>>>

TBI remains a challenge within modern trauma systems, not only due to its contribution to mortality but also due to
the magnifying impact on the outcome because of small process deviations. Delays in imaging, inconsistent airway
management, and lapses in haemodynamic measures are all examples that can result in irreversible damage. Although
TQIP have been developed to identify and correct such lapses, with the WHO stressing the importance of linking OFIs
to corrective actions and verification of bettered outcomes, most research has been done on mixed trauma cohorts.
This, on the other hand, leaves TBI-specific vulnerabilities undercharacterised. Recent work by *Szolnoky et al.*
suggests that, despite overall declines in OFI, patients with TBI remain at risk of preventable shortcomings,
underscoring the need for TBI-specific quality improvement efforts [@Szolnoky2025]. Therefore, we
hypothesise that despite existing trauma quality improvement measures, new OFIs can be identified in
the care of adult trauma patients with TBI.

Aim
=====
As such, this study aims to determine whether OFIs occur in the care of adult trauma patients with
TBI, and, if so, to quantify their frequency, describe their characteristics, and examine whether
patient- and process-related factors are associated with their occurrence.

@@

Participants
------------
Included in the study were all adult patients with TBI recorded in the Karolinska trauma registry between 2012 and
2023 who also had been screened for opportunity for improvements. Furthermore, TBI was defined as a Glasgow Coma
Scale (GCS) score of ≤8 combined with an Abbreviated Injury Scale (AIS) severity ≥3 for the head region.
Patients were eligible irrespective of level of care and were not restricted to intensive care admissions.
